---
title: "Friends Project - Progress Report"
author: "Wenyang Cao, Wenling Zhou, Sixuan Li, Haoran Yang"
date: "2024-03-01"
output: 
  html_document: 
    theme: united
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment="", warning = FALSE, message = FALSE, tidy.opts=list(width.cutoff=55), tidy = TRUE)
```


## Introduction
Friends is a sitcom featuring the lives of six young people, following the lives of three men and three women living in New York City - Monica, Chandler, Rachel, Phoebe, Joey, and Ross - from the time they first meet to the time they experience life together ten years later. Through the interactions and experiences of the characters in "Friends," audiences can see stories that reflect various real-life themes and issues, including the nature of friendship, the complexities of love, the challenges of career advancement, and the journey of growth and self-discovery. These themes run throughout the episode, allowing viewers to laugh and think deeply about life's various emotions and challenges.

Like many people's adolescence, "Friends” directly looks at what life is like for young people. It teaches us to love passionately, not condemn ourselves, and to praise and criticize others sincerely. The six characters in the show come from different backgrounds and have different personalities. Still, their sincerity in friendship, courage in facing their feelings and challenges, and seriousness in self-reflection all leave a deep impression. Each character experiences the influence of their family of origin, their relationship with their parents, and the fluctuation of different emotions and friendships, and these plots resonate with the audience because they are close to reality.

## Research Questions 
Current research lacks in providing a detailed analysis of verbal and emotional expression in Friends, particularly in quantifying the distribution of love and positive emotions among the characters. The first research question for this project is to determine which character expresses love most often or has the most positive attitude based on analyzing each character's dialogue. Specifically, we will explore the complexity of the conversation between the characters and relate it to their backgrounds and caring personalities to determine which character shows the most emotional expression and positive attitude.  Research in this way can help us analyze the individuality of each character and lead to a deeper understanding of their role and development in the plot of the story.

The second research question is still through the study of dialogues of “Friends”, we will explore in depth how each character's different cultural or social backgrounds are reflected in their dialogues. This includes analyzing their language styles, diction habits, and topics related to a particular regional culture. For example, there are linguistic differences between native New Yorkers and outsiders, as well as the slang and catchphrases that different characters may use, thus reflecting their regional cultural backgrounds. 

## Literature review（Plan a）
Previous research on the sitcom "Friends" has explored various aspects of the show, including analyses of character identities, gender representations, and cultural impacts.  However, there remains ample opportunity for further analysis, particularly with regards to using computational linguistics methods to study the show's dialogue.

In terms of analyzing emotional expression and positive attitude, most research has relied on qualitative methods.  For example, Lieberman (2022) conducted a discourse analysis of empathy among the core characters, while Shukla (2020) examined relationship dynamics between Ross and Rachel through a social constructionist lens.  However, computational analysis of emotionality and sentiment in the dialogue has been limited.  Jamali and Abadeh (2021) used sentiment analysis to compare positivity in male versus female speech, but did not analyze individual characters.  Applying sentiment analysis tools to Friends could reveal new insights regarding each character's emotionality and outlook.

Regarding the use of language to signify regional culture and identity, Friends has been critiqued for lack of diversity, as all six main characters are white (Song, 2020).  However, through linguistic analysis, the show does indirectly reference different American subcultures.  For example, Modleski (2003) deconstructs "New York style" versus "California speak" between Monica and Phoebe based on their word choices and topics discussed.  Still, computational tools could systematically analyze lexical and semantic differences in language use by characters, shedding light on the indirect representation of regional identities.  Complementary analytic methods like topic modeling may also uncover patterns in how cultural references emerge through natural dialogue.

In summary, while Friends has been extensively studied from qualitative lenses, computational text analysis remains an underexplored methodology with high potential.  Sentiment analysis could quantify positivity of characters, and lexicographic comparisons may reveal subtle markers of cultural background.  Such computational linguistics methods can uncover fresh patterns from the decades-old show.  Integrating qualitative contextualization with broader computational inquiry promises a richer understanding of identity, emotion, and culture encoded within Friends' famously funny dialogue.

## Data Cleaning


## Data Summary 


### Session Info:
```{r}
sessionInfo()
```


